---
title: "simpleRegress"
author: "Trevor Ragazzo "
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

We see a result of the longer the x axis goes the higher Y value gets higher. which means we get a higher lengthed than neck value 

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

From all three results we see a increase from left to right. 


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(CHEST~NECK,data=bears)
plot(CHEST~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Now we compared neck and chest to see a closer result rather than neck and length. With this graph we still see an increse but alot of plots scrattered more center than compared to length. 


